\raceentry{Drow}{``Time to die for the Spider Queen."}
\begin{multicols}{2}
Throughout most of the subterranean world the dominant powers are the nation-states of the drow. Also known as ``dark elves", drow are the prototypical malevolent race of intelligent villains who dwell in the shadows and dark places of the world. Drow as characters are usually enemies, or if not, outcasts from drow society.
\racedescription{Females tend to be bigger and stronger than males. Drow are characterized by white or silver hair and obsidian black skin. Their eyes are red (or rarely gray, violet, or yellow) in darkness and green in normal light. Otherwise they physically resemble their elvish cousins.}
\racepersonality{In a word, selfish. Drow aren't remarkably different from humans in their outlook on life, save that they care very little for the world as a whole or the benefit of society. Instead they care only for themselves and what benefits the individual drow's appetites. Most drow place no importance on love, loyalty, honesty, or integrity. Instead, survival belongs to the strong who are capable of outliving their enemies and rivals. Murder, especially in secret, is very common, and much of a drow's energies are put into ensuring that they are better at murder and avoiding being murdered than everyone they know. While drow are as capable as elves of living many centuries before they could be considered old, the average lifespan of a drow is barely greater than that of a human.}
\racesociety{Drow society is a matriarchal theocracy dominated by the priestesses of The Spider Queen, Lolth. Outside the circles of the entirely female religious elite, power is held primarily in the hands of those conniving enough to secure the endorsement of the church and wealth enough to avoid assassination. Drow men are not allowed to be priests and are less likely to hold high positions of power than drow women, but most practitioners of arcane magic are men. Freedom is not a respected right, but is a decadence gained only through power. Cruelty, slavery, and control by the threat of violence are the norm in drow cities.}
\racealignment{Drow are evil. Not that they are born that way or that there cannot be the occasional exception, but the chances of someone with a less-than-selfish (or worse, honorable) outlook on life surviving in drow society are minimal, especially among those who more zealously worship their evil goddess Lolth. Their society instills an element of chaos as well, tempered only by Lolth's continuing vigilence against those who would destroy drow society. Besides, everyone --- even the drow --- assume that every drow is evil.}

\columnbreak

\begin{racetable}
\type{Humanoid (Elf subtype)}
\size{Medium}
\scores{+2 Dexterity, --2 Constitution}
\speed{30}
\senses{Darkvision 120'}
\racialtraits{
\racetrait{Daylight Sensitivity}{While in brightly lit surroundings (such as a daylight spell), a Drow suffers a -2 penalty to attack rolls and precision-based skill checks.}
\racetrait{Innate Magic}{Drow with a Charisma of at least 10 may cast deeper darkness (duration 4 hours), and fairie fire as spell-like abilities with a caster level equal to their character level once per day each.}
\racetrait{Magic Resistant}{+2 bonus to saving throws against spells and spell-like abilities.}
\racetrait{Skill Bonus}{+2 bonus to Spot and Listen checks.}
\racetrait{Elven Trance}{Drow never sleep and are immune to sleep effects. Drow must still perform their 4 hour daily trance to stay coherent and rested.}
\racetrait{Interesting Times}{Drow live an exceedingly interesting life and every Drow has proficiency with the rapier and an exotic ranged weapon of their choice.}
}
\autolanguages{Elvish, Undercommon}
\bonuslanguages{Abyssal, Beholder, Common, Draconic, Drow Sign Language, Dwarvish, Gnome, Kuo-Toa, Terran}
\favoredclasses{Cleric and Wizard}
\end{racetable}

\vspace{\baselineskip}
\agetable{20}{+1d6}{+2d6}{+3d6}

\vspace{\baselineskip}
\begin{heightweighttable}
\male{4' 7"}{+2d8}{90 lb.}{x(2d4)}
\female{4' 5"}{+2d8}{80 lb.}{x(2d4)}
\end{heightweighttable}
\end{multicols}